---
title: Template Presentacion 
subtitle: Copia varios repositorios
author: Jhon Flores Rojas
institute: UNCP
date: "`r format(Sys.time(), '%d %m, %Y')`"
output:
  beamer_presentation:
    includes:
      in_header: t1.tex
    theme: CambridgeUS
    colortheme: lily
    slide_level: 2
    incremental: true # numeraciones 
    #keep_tex: true
    #keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

# R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

# Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

# Slide with Plot

```{r pressure}
plot(pressure)
```


## algo 

falksjfowie uroiewurw

### decir

ecuacion $Euler$

